5_data_viz

### 2018-05-30 scripts/5_data_viz.Rmd
Reorg: deprecate plots and functions

---
title: "5_data_viz"
author: "Andy Krause"
date: "May 10, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   revdens <- ggplot(rev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

   # Add together for plotting potential revenues
   prev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, gross_revenue=pot_revenue) %>%
                         dplyr::mutate(tenure = 'str'),
                       ltr_tdf %>%
                         tidyr::unnest() %>%
                         dplyr::select(type, gross_revenue) %>%
                         dplyr::mutate(tenure = 'ltr'))

   prevdens <- ggplot(prev_df, 
                     aes(x=gross_revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=c(ltr_col, str_col)) +
    scale_color_manual(values=c(ltr_col, str_col)) +
    ggtitle('Annual Revenues by Tenure Type') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))

@@

The location of the short and long term rentals, colored by submarket, are shown below

```{r locationmaps.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

 # Set submarket colors
   # Make map
  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(ltr_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.02, shape=15)

  tm_shape(sub_sf) +
    tm_polygons() + 
  tm_shape(study_area) + 
    tm_polygons(col='dodgerblue3') +
  tm_shape(str_sf) +
    tm_symbols(size=.05, col='black', border.alpha=0, alpha=.2, shape=15)

  str_map <- ggplot() +
     geom_polygon(data=ssub_sf, aes(x=long, y=lat, group=group), fill='white', color='grey70') 
#     geom_point(data=str_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.2,
#                alpha=.2) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Short-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r ltr.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}
# 
#   # Make map
# 
#   ltr.map <- ggplot() +
#     geom_polygon(data=subs, aes(x=long, y=lat, group=group), fill='white', color='grey70') +
#     geom_point(data=ltr_df, aes(x=longitude, y=latitude, color=geo.mrkt), size=.1,
#                alpha=.1) +
#     scale_color_manual(values=sm_col) +
#     scale_x_continuous(limits=c(min(subs$long), max(subs$long))) +
#     scale_y_continuous(limits=c(min(subs$lat), max(subs$lat))) +
#     xlab('') + ylab('')+
#     theme(legend.position = 'bottom',
#           legend.title = element_blank(),
#           plot.title = element_text(hjust = 0.5),
#           panel.grid.major = element_blank(),
#           panel.grid.minor = element_blank(),
#           panel.background = element_rect(fill = "white"),
#           axis.text.x = element_blank(),
#           axis.text.y = element_blank(),
#           axis.ticks = element_blank(),
#           axis.title.x=element_blank(),
#           axis.title.y=element_blank(),
#           panel.border = element_rect(colour = "black", fill=NA, size=1)) +
#     guides(colour = guide_legend(override.aes = list(size=3,
#                                                      alpha=1))) + 
#     ggtitle('Long-Term Rental Locations')+
#     theme(plot.title = element_text(hjust = 0.5))
#   
# ```
# 
# ```{r loc.plot, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE, fig.width=9}
#   
#   png(file=paste0(fig.path, 'str_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      str.map
#   dev.off()
#   
#   png(file=paste0(fig.path, 'ltr_locmap.png'), width = 680, height = 590, 
#       bg='transparent')
#      ltr.map
#   dev.off()
# 
#   ggMultiPlots(str.map, ltr.map, cols=2)
#   
#   save(str.map, file=paste0(fig.path, 'strMap.RData'))
#   save(ltr.map, file=paste0(fig.path, 'ltrMap.RData'))
# 
```
#

@@

   strtype.map <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

@@

   ltrtype.map <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=abb_col[c(1,3,5,7,9)]) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     #ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

@@

# The chart below break down the relative frequency of short and long term rental properties across the five submarkets. 
#

<!-- Having calculated the revenues, both short-term and long-term imputed, we now compare the actual (extr), potential and imputed long-term revenue distributions for the short term properties  -->

<!-- ```{r plot_revdens, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=6,fig.height=3.5} -->

<!--   # Actual -->
<!--    stra.rev <- str_df.ic[,c('property.id', 'str.act.revenue')] -->
<!--    stra.rev$tenure <- 'Short-Term (Actual)   ' -->
<!--    names(stra.rev)[2] <- 'revenue' -->

<!--   # Potential -->
<!--    strp.rev <- str_df.ic[,c('property.id', 'str.pot.revenue')] -->
<!--    strp.rev$tenure <- 'Short-Term (Potential)   ' -->
<!--    names(strp.rev)[2] <- 'revenue' -->

<!--   # Long-Term -->
<!--    ltr.rev <- str_df.ic[,c('property.id', 'ltr.imp.revenue')] -->
<!--    ltr.rev$tenure <- 'Long-Term   ' -->
<!--    names(ltr.rev)[2] <- 'revenue' -->

<!--   # Combine -->
<!--    revdens.data <- rbind(stra.rev, strp.rev, ltr.rev) -->

<!--   ## Build a plot -->

<!--    rd.plot <- ggplot(revdens.data,  -->
<!--                      aes(x=revenue, fill=tenure, color=tenure)) + -->
<!--      geom_density(alpha=.5) + -->
<!--      scale_fill_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
<!--      scale_color_manual(values=c(ltr.col, abb.col[2], str.col)) + -->
<!--      xlab('\nAnnual Revenue') + -->
<!--      scale_x_continuous(breaks=c(seq(0, 75000, by=25000)), -->
<!--                         labels=c('$0', '$25k', '$50k', '$75k'))+ -->
<!--      theme(legend.position='none', -->
<!--            legend.title = element_blank(), -->
<!--            plot.title = element_text(hjust = 0.5), -->
<!--            axis.text.y = element_blank(), -->
<!--            axis.ticks.y = element_blank(), -->
<!--            axis.title.y=element_blank()) + -->
<!--      coord_cartesian(xlim=c(0, 85000)) -->
<!--      rd.plot <- rd.plot + facet_wrap(~tenure) -->

<!--   ## Plot -->

<!--      rd.plot -->

<!-- ``` -->

<!-- ## Results -->

<!-- Next, we plot the \% of properties that have short-term preference versus the occupancy rate as occupancy rate is an important determinant of short-term preference.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Set Preference data field -->

<!--   str_df.ic$pref <- str_df.ic$str.act.pref -->

<!--  ## Calculate the percentile fields -->

<!--   str_df.ic$occ.qtl <- makeWtdQtl(str_df.ic$occ.rate,  -->
<!--                                       return.type='rank')  -->
<!--   str_df.ic$rate.qtl <- makeWtdQtl(str_df.ic$med.rate,  -->
<!--                                   return.type='rank')  -->

<!--  ## Calculate raw and percentile occupancies -->

<!--   rawocc.metro <- abbPrefPlot(str_df.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5) -->

<!--   qtlocc.metro <- abbPrefPlot(str_df.ic, -->
<!--                         x.field='occ.qtl', -->
<!--                         smooth=TRUE, -->
<!--                         smooth.span=.5) -->

<!--    ## Make plots   -->

<!--   # Raw -->
<!--   raw.occ.metro <- ggplot(rawocc.metro$data, -->
<!--                    aes(x=x.var, y=Var))+ -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') +  -->
<!--     ggtitle('Raw Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Quantile -->
<!--   qtl.occ.metro <- ggplot(qtlocc.metro$data, -->
<!--                    aes(x=x.var, y=Var))+ -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') +  -->
<!--     ggtitle('Percentile Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--   # Make Plot -->
<!--   ggMultiPlots(raw.occ.metro, qtl.occ.metro, cols=2) -->

<!-- ``` -->

<!-- Next we build a heat map that shows which combinations of occupancy rate and nightly rate are most likely to result in short-term preference. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   rate.hm <- abbHeatMap(str_df.ic, -->
<!--                 x.field='occ.rate', -->
<!--                 y.field='med.rate', -->
<!--                 pref.field='str.act.pref', -->
<!--                 svm=F,  -->
<!--                 alpha.count=T, -->
<!--                 add.points=T, -->
<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   rate.hm + ylab('Nightly Rate') -->

<!-- ``` -->

<!-- To make the distinction more clear, we employ a Support Vector Machine to classify the areas into short and long term preference.  -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   rate.hm.svm <- abbHeatMap(str_df.ic, -->
<!--                             x.field='occ.rate', -->
<!--                             y.field='med.rate', -->
<!--                             pref.field='str.act.pref', -->
<!--                             svm=T,  -->
<!--                             alpha.count=F, -->
<!--                             add.points=T, -->
<!--                             fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   rate.hm.svm+ ylab('Nightly Rate') -->

<!-- ``` -->

<!-- As the distributions of occupancy rate and nightly rate are not uniform, we standardize these values to a percentile and then replot to give a better sense of the relative level of occupancy rate and nightly rate required for short-term preference. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   qtl.hm <- abbHeatMap(str_df.ic, -->
<!--                 x.field='occ.qtl', -->
<!--                 y.field='rate.qtl', -->
<!--                 pref.field='str.act.pref', -->
<!--                 svm=F,  -->
<!--                 alpha.count=T, -->
<!--                 add.points=T, -->
<!--                 fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   qtl.hm+ ylab('Nightly  (Pcntl)') -->

<!-- ``` -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   qtl.hm.svm <- abbHeatMap(str_df.ic, -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T,  -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) -->
<!--   qtl.hm.svm+ ylab('Nightly  (Pcntl)') -->

<!-- ``` -->

<!-- ### Submarkets -->

<!-- Now we move on to looking more deeply at various submarkets.  We start by analyzing the differences between houses and apartments.  -->

<!-- First we make a comparison table of the results.   -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--  # Make Basic comparison table -->
<!--   pref.table.type <- abbCreateCompTable(ic.df=str_df.ic, -->
<!--                                    split.field='type') -->

<!--  # Limit to the extrapolated pref type -->
<!--   pref.table.type <- pref.table.type[pref.table.type$rev.type == 'Actual', ] -->

<!-- ``` -->

<!-- We then turn this into a simple chart to see the differences. -->

<!-- ```{r message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=TRUE} -->

<!--   ggplot(pref.table.type, aes(x=ID, weights=Var, fill=ID)) +  -->
<!--     geom_bar() + -->
<!--     scale_fill_manual(values=c('red', 'blue')) + -->
<!--     xlab('') + -->
<!--     ylab('% of properties where Airbnb is more profitable') + -->
<!--     scale_y_continuous(breaks=c(0,.25,.5,.75,1), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='none') -->

<!-- ``` -->

<!-- We then look at the relationship between occ rate and preference.  Before we start though we recalculate the percentiles within each submarket.  -->

<!-- ```{r build_occ_type1, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Create dataset -->

<!--   type.data.ic <- str_df.ic -->

<!--   # Id the types -->
<!--   apt.id <- which(str_df.ic$type == 'Apartment') -->
<!--   house.id <- which(str_df.ic$type == 'House') -->

<!--   # Recalculate the percentiles -->
<!--   type.data.ic$occ.qtl[apt.id] <- makeWtdQtl(type.data.ic$occ.rate[apt.id], -->
<!--                                       return.type='rank') -->
<!--   type.data.ic$occ.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$occ.rate[house.id], return.type='rank') -->

<!--   type.data.ic$rate.qtl[apt.id] <- makeWtdQtl(type.data.ic$med.rate[apt.id], -->
<!--                                   return.type='rank') -->
<!--   type.data.ic$rate.qtl[house.id] <- makeWtdQtl( -->
<!--     type.data.ic$med.rate[house.id], return.type='rank') -->

<!-- ```  -->

<!-- Then we calculate the preference figures -->

<!-- ```{r build_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE} -->

<!--  ## Calc the occ rate numbers -->

<!--   rawocc.type <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.rate', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!--   pctocc.type <- abbPrefPlot(type.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='type', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=c('black', 'grey40')) -->

<!-- ``` -->

<!-- And then plot.  -->

<!-- ```{r plot_occ_type, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=FALSE, fig.width=7, fig.height=3.5, fig.cap='\\label{smocc}Preference vs Occ. Rates: By Type'} -->

<!--  ## Build raw plot -->

<!--   ptr.occ <- ggplot(rawocc.type$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate') + -->
<!--     scale_color_manual(values=c('black', 'grey60'), -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Raw Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--  ## Build Percentile Plots -->

<!--   ptq.occ <- ggplot(pctocc.type$data, -->
<!--                     aes(x=x.var, y=Var, group=ID, color=ID)) +   -->
<!--     geom_point(alpha=.5, size=.4) + -->
<!--     stat_smooth(se=FALSE, size=2, span=.5) + -->
<!--     xlab('\nOccupancy Rate (Pcntl)') + -->
<!--     scale_color_manual(values=c('black', 'grey60'), -->
<!--                        name='') + -->
<!--     scale_x_continuous(breaks=seq(0, 100, by=25), -->
<!--                        labels=c('0%', '25th', '50th', '75th', '100th')) + -->
<!--     ylab('\nSTR Preferability %') + -->
<!--     scale_y_continuous(breaks=seq(0, 1, by=.25), -->
<!--                        labels=c('0%', '25%', '50%', '75%', '100%')) + -->
<!--     theme(legend.position='bottom') +  -->
<!--     ggtitle('Percentile Rates') +  -->
<!--     theme(plot.title = element_text(hjust = 0.5)) -->

<!--  ## Plot   -->

<!--   ggMultiPlots(ptr.occ, ptq.occ, cols=2) -->

<!-- ``` -->

<!-- Finally, we make percentile SVM heatmaps for both apartments and houses.  -->

<!-- ```{r plot_svm_type, fig.width=8, fig.height=3.5, echo=FALSE, fig.cap='\\label{smhm}Analysis of Percentile Rates: By Type'} -->

<!--  ## Make House SVM Heatmap -->

<!--   house.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
<!--                                           'House', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5])) + -->
<!--   theme(legend.position='none') + -->
<!--   annotate("text", x = 50, y = 50, label = "Houses", size=9) + -->
<!--   ylab('Nightly Rate (Pcntl)') + -->
<!--   xlab('Occupancy Rate (Pcntl)') -->

<!--  ## Make Apartment SVM Heat Map -->

<!--   apt.hm.svm <- abbHeatMap(type.data.ic[type.data.ic$type == -->
<!--                                           'Apartment', ], -->
<!--                    x.field='occ.qtl', -->
<!--                    y.field='rate.qtl', -->
<!--                    pref.field='str.act.pref', -->
<!--                    svm=T, -->
<!--                    alpha.count=F, -->
<!--                    add.points=T, -->
<!--                    quantile=T, -->
<!--                    fill.colors=c(abb.col[1], abb.col[5]))+ -->
<!--   theme(legend.position='none')+ -->
<!--   annotate("text", x = 50, y = 50, label = "Apartments", size=9)+ -->
<!--   ylab('Nightly Rate (Pcntl)') + -->
<!--   xlab('Occupancy Rate (Pcntl)') -->

<!--  ## Plot -->

<!--   ggMultiPlots(house.hm.svm, apt.hm.svm, cols=2) -->

<!-- ``` -->

<!-- #### Geographic Submarkets -->

<!-- We now repeat the three analyses -- table, occupancy plot, heat map -- for the five geographic submarkets. -->

<!-- ```{r table_geo, message=FALSE, warning=FALSE, results='asis', comment=FALSE, cache=TRUE, echo=FALSE, fig.cap='Geographic Submarket Preferability'} -->

<!--  # Make Basic comparison table -->
<!--   pref.table <- abbCreateCompTable(ic.df=str_df.ic, -->
<!--                                    split.field='geo.mrkt') -->

<!--  # Convert to wide format for output -->
<!--   pref.table.wide <- dcast(pref.table, ID ~ rev.type, value.var='Var') -->

<!--  # Limit to the extrapolated pref type -->
<!--   pref.table <- pref.table[pref.table$rev.type == 'Actual', ] -->
<!--   pref.table[ ,1] <- c('City-Core', 'City', 'Suburban', 'Rural', 'Beach') -->
<!--   pref.table[ ,2] <- paste0(sprintf('%.1f', pref.table[ ,2] * 100), '%') -->

<!--  # Fix names   -->
<!--   names(pref.table) <- c('Sub-Market', 'Short-Term Preferable') -->
<!--   options(xtable.comment = FALSE) -->

<!--  ## Make printable table -->

<!--   print(xtable(pref.table[,1:2],  -->
<!--                caption='Geographic Submarket Preferability\n', -->
<!--                digits=1, -->
<!--                align='llr'), -->
<!--         include.rownames=FALSE, -->
<!--         caption.placement='top') -->

<!-- ``` -->

<!-- ```{r build_occ_geo, fig.width=8, fig.height=4, echo=FALSE}  -->

<!--  ## Build data -->

<!--   subm.data.ic <- str_df.ic -->

<!--   # Get IDs -->
<!--   cc.id <- which(str_df.ic$geo.mrkt == 'city-core') -->
<!--   city.id <- which(str_df.ic$geo.mrkt == 'city') -->
<!--   sub.id <- which(str_df.ic$geo.mrkt == 'suburban') -->
<!--   rural.id <- which(str_df.ic$geo.mrkt == 'rural') -->
<!--   beach.id <- which(str_df.ic$geo.mrkt == 'beach') -->

<!--   # Recalc the percentiles -->
<!--   subm.data.ic$occ.qtl[cc.id] <- makeWtdQtl(subm.data.ic$occ.rate[cc.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[cc.id] <- makeWtdQtl(subm.data.ic$med.rate[cc.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[city.id] <- makeWtdQtl( -->
<!--       subm.data.ic$occ.rate[city.id], return.type='rank') -->
<!--   subm.data.ic$rate.qtl[city.id] <- makeWtdQtl( -->
<!--     subm.data.ic$med.rate[city.id], return.type='rank') -->

<!--   subm.data.ic$occ.qtl[sub.id] <- makeWtdQtl(subm.data.ic$occ.rate[sub.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[sub.id] <- makeWtdQtl(subm.data.ic$med.rate[sub.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[rural.id] <- makeWtdQtl(subm.data.ic$occ.rate[rural.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[rural.id] <- makeWtdQtl(subm.data.ic$med.rate[rural.id], -->
<!--                                   return.type='rank') -->

<!--   subm.data.ic$occ.qtl[beach.id] <- makeWtdQtl(subm.data.ic$occ.rate[beach.id], -->
<!--                                       return.type='rank') -->
<!--   subm.data.ic$rate.qtl[beach.id] <- makeWtdQtl(subm.data.ic$med.rate[beach.id], -->
<!--                                   return.type='rank') -->

<!-- ``` -->

<!-- ```{r plot_occ_geo, fig.width=9, fig.height=4, message=FALSE, warning=FALSE, echo=FALSE, fig.cap='\\label{smocc}Analysis of Percentile Rates: Geographic Submarkets'}  -->

<!--  ## Set colors -->

<!--   sm.col <- abb.col[c(1, 3, 6, 5, 2)]  -->

<!--  ## Create plot data -->

<!--   rawocc.geo <- abbPrefPlot(subm.data.ic, -->
<!--                         x.field='occ.rate', -->
<!--                         split.field='geo.mrkt', -->
<!--                         smooth=TRUE, -->
<!--                         smooth.span=.5 , -->
<!--                         spl.col=sm.col) -->

<!--   pctocc.geo <- abbPrefPlot(subm.data.ic, -->
<!--                          x.field='occ.qtl', -->
<!--                          split.field='geo.mrkt', -->
<!--                          smooth=TRUE, -->
<!--                          smooth.span=.5 , -->
<!--                          spl.col=sm.col) -->

<!--  ## Make plot objects   -->

>>>>

---
title: "5_data_viz"
author: "Andy Krause"
date: "May 10, 2018"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

  knitr::opts_chunk$set(echo = TRUE)

@@

```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  library(tmap)
  library(magrittr)
  library(dplyr)
  library(ggplot2)

```{r load_data, message=FALSE, warning=FALSE, comment=FALSE, cache=TRUE, echo=FALSE, results='hide'}

  load(file.path(getwd(), 'data', 'analyzed', 'analyzed_data.RData'))

  dir.create(file.path(getwd(), 'images'))

  str_col = col_df$rgb[1]

## Suburb Location Map

```{r sub_loc.map, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  # Set submarket colors
  suburb_sf$col <- 'gray80'
  suburb_sf$col[suburb_sf$class == 'Middle'] <- 'gray50'
  suburb_sf$col[suburb_sf$class == 'Inner'] <- 'gray20'

   # Make map

  png(filename = file.path(getwd(), 'images', "sub_loc_map.png"), 
       width = 6.5, height = 6.5, units = 'in', res = 300)

  tm_shape(suburb_sf) +
    tm_polygons("class", palette=c('gray20', 'gray50', 'gray80'), title='Suburb Class') +
  tm_shape(studyarea_sf) + 
    tm_borders(col='black', lwd=5) +
    tm_add_legend(type='fill', border.lwd=3, col='white', border.col='black',
                  title='Study Area')

## Point Location Maps

```{r location map}

  sm_col <- c(col_df$rgb[3], col_df$rgb[4], col_df$rgb[5], 
              col_df$rgb[6], col_df$rgb[1])

  png(filename = file.path(getwd(), 'images', "ltr_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(ltr_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16, legend.col.show=TRUE)
  dev.off()

  png(filename = file.path(getwd(), 'images', "str_loc_map.png"), 
       width = 4, height = 4, units = 'in', res = 300)
  tm_shape(studyarea_sf) + 
    tm_borders(col='gray50', lwd=2) +
  tm_shape(suburb_sf %>% dplyr::filter(in_studyarea == 1)) +
    tm_borders(col='gray90', lwd=.5) +
  tm_shape(str_sf %>% dplyr::rename(Submarket = geo_mrkt)) +
    tm_symbols('Submarket', size=.02,
               palette = sm_col, alpha=.3, shape=16)
  dev.off()

@@

   strtype_bar <- ggplot() +
     geom_bar(data=str_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col, name='Submarket') +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Short Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

@@

   ltrtype_bar <- ggplot() +
     geom_bar(data=ltr_tdf, aes(x=geo_mrkt, fill=geo_mrkt)) +
     scale_fill_manual(values=sm_col) +
     facet_wrap(~type) +
     ylab('# of Properties\n') + xlab('')+
     theme(legend.position = 'bottom',
           legend.title = element_blank(),
           axis.text.x=element_blank(),
           axis.ticks.x=element_blank()) +
     ggtitle('Long Term Property Type\nBy Submarket')+
     theme(plot.title = element_text(hjust = 0.5))

     png(filename = file.path(getwd(), 'images', "loc_bar.png"), 
       width = 8, height = 4, units = 'in', res = 300)

     ggMultiPlots(strtype_bar, ltrtype_bar, cols=2)
     dev.off()

@@

```{r maps}

   dens_cols <- c(col_df$rgb[3], col_df$rgb[1], col_df$rgb[2])

   # Add together for plotting
   rev_df <- bind_rows(str_tdf %>% 
                         dplyr::select(type, revenue=lik_revenue_net) %>%
                         dplyr::mutate(tenure = 'Short Term (Likely)   ',
                                       alpha = .5),
                       str_tdf %>% 
                         dplyr::select(type, revenue=pot_revenue_net) %>%
                         dplyr::mutate(tenure = 'Short Term (Potential)   ',
                                       alpha = .4),
                       ltr_df %>%
                         dplyr::select(type, revenue=gross_revenue) %>%
                         dplyr::mutate(tenure = 'Long-Term   ',
                                       alpha = .9))

  png(filename = file.path(getwd(), 'images', "rev_dens.png"), 
       width = 5.5, height = 4, units = 'in', res = 300)

   ggplot(rev_df,
          aes(x=revenue, fill=tenure, color=tenure)) +
    geom_density(alpha=.5) +
    scale_fill_manual(values=dens_cols) +
    scale_color_manual(values=dens_cols) +
    ggtitle('Short Term Revenue vs Long Term Revenue') +
    xlab('Annual Revenue') +
    scale_x_continuous(breaks=c(seq(0,60000, by=20000)),
                       labels=c('$0', '$20,000', '$40,000', '$60,000'))+
    theme(legend.position='bottom',
          legend.title = element_blank(),
          plot.title = element_text(hjust = 0.5),
          axis.text.y = element_blank(),
          axis.ticks.y = element_blank(),
          axis.title.y=element_blank()) +
    coord_cartesian(xlim=c(0, 70000))
